Proportional multi-state multiple-cohort life table model

### 2018-04-19 MSLT/MSLTdoc.Rmd
Added original data to interpolated data graphs

assign(paste(sex_index, measure_index, "interpolated", sep = "_"), interpolated)
plot(interpolated$age,interpolated$rate)

###Do graph with another layer for original rates in age groups for comparison purposes. 
 # p <- ggplot(data = interpolated, aes(age,rate)) +
 #            geom_line(aes(color = "Interpolated")) 
 #            theme_classic()
 #            print(p)
  }
}

>>>>

assign(paste(sex_index, measure_index, "interpolated", sep = "_"), interpolated)
# plot(interpolated$age,interpolated$rate)

##Do graph with another layer for original rates in age groups for comparison purposes.
p <- ggplot() +
            geom_line (
              data = interpolated,
              mapping = aes(ages,rate) 
              ) +
              geom_point(
                data = data, 
                mapping = aes(age_cat, one_rate)
                ) +
           theme_classic()
           print(p)
  }
}
